PTFO 8-8695: Two Stars, Two Signals, No Planet

### 2020-04-27 paper/ms.tex
update manuscript

We begin in Section~\ref{sec:observations} by describing newly
available observations from TESS \citep{ricker_transiting_2015} and
Gaia \citep{gaia_collaboration_gaia_2018}.  The TESS lightcurve shows
two different periodic signals, which we analyze in
Section~\ref{sec:tess}.
The Gaia data, analyzed in Section~\ref{sec:gaia}, show that
\ptfo\ is a photometric binary, and suggest it also an astrometric binary.
We discuss the pieces of the puzzle
in Section~\ref{sec:discussion}, and summarize the situation in
Section~\ref{sec:conclusions}.
We comment on the
concurrent study by \citet{koen_2020} in postscript.

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.99\textwidth]{f3.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Phase-folded longer and shorter-period signals.}
    {\it Top}: Longer-period signal, as in Figure~\ref{fig:splitsignal}.
    {\it Bottom}: Shorter-period signal. The reference phase is set to
    the dip.  Gray points are the 10 minute cadence
    \texttt{PDCSAP} flux.  Black points are binned to 100 points per
    period.
		\label{fig:phasefold}
	}
\end{figure*}

>>>>

We begin in Section~\ref{sec:observations} by describing newly
available observations from TESS \citep{ricker_transiting_2015} and
Gaia \citep{gaia_collaboration_gaia_2018}.  The TESS lightcurve shows
two different periodic signals, which we analyze in
Section~\ref{sec:tess}.
The Gaia data, analyzed in Section~\ref{sec:gaia}, show that
\ptfo\ is a photometric binary, and suggest it also an astrometric binary.
We discuss the pieces of the puzzle
in Section~\ref{sec:discussion}, and summarize the situation in
Section~\ref{sec:conclusions}.
We comment on the
study by \citet{koen_2020} in postscript.

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.99\textwidth]{f3.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Phase-folded longer and shorter-period signals.}
    {\it Top}: Relative flux at the longer-period, as in Figure~\ref{fig:splitsignal}.
    {\it Bottom}: Shorter-period signal. The reference phase is set to
    the dip.  Gray points are the 10 minute cadence
    \texttt{PDCSAP} flux.  Black points are binned to 100 points per
    period.
		\label{fig:phasefold}
	}
\end{figure*}
